### 2021-12-03 input/proposal.tex
notes

\begin{definition}[\label{def:fbplus}FB$^+$: echos] FB where a
  \process $x$ that receives a stale message sends back --~or
  echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'})$ with
  $\alpha_{s'} = \min D_x \wedge \delta_{s'} \not\in D_x$.
\end{definition}

@@

\begin{lemma}[\label{lem:detector}$\textup{FB}^+ \wedge \textup{FS}
  \implies$ \underline{D}etector existence (D)]
  Assuming $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on
  $\pi_{xz}$ of $\alpha_x$ with $\alpha_x = \min D_z$, if $x$
  broadcasts a staleness notification $\delta_x$, either $z$
  eventually delivers it, or a \process $y$ in such a chain of
  delivery $\pi_{xz}'$ eventually detects its blocking.
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}

@@

\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \wedge \textup{D} \implies \textup{DCP}$]
  A protocol guarantees dynamic consistent partitioning if it
  implements forwarding of best up-to-date messages with echos,
  forwarding of staleness messages downstream, and detection of
  possible blocking of staleness notifications.
\end{theorem}

>>>>

\begin{definition}[\label{def:fbplus}FB$^+$: echos] FB where a
  \process $x$ that receives a staleness notification sends back --~or
  echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'})$ with
  $\alpha_{s'} = \min D_x \wedge \delta_{s'} \not\in
  D_x$. \TODO{Rework min}
\end{definition}

\TODO{Naive implementation is FB$^+$ etc. It does not work.}

@@

\begin{lemma}[\label{lem:detector}$\textup{FB}^+ \wedge \textup{FS}
  \implies$ \underline{D}etector existence (D)] Assuming
  $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on $\pi_{xz}$ of
  $\alpha_x$ with $\alpha_x = \min D_z$, if $x$ broadcasts a staleness
  notification $\delta_x$, either $z$ eventually delivers it, or a
  \process $y$ in such a chain of delivery $\pi_{xz}'$ eventually
  \TODO{detects} its \TODO{blocking}.
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}

@@

\TODO{$FB \subseteq FB+$}.

\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \TODO{\wedge \textup{D}} \implies \textup{DCP}$]
  A protocol guarantees dynamic consistent partitioning if it
  implements forwarding of best up-to-date messages with echos,
  forwarding of staleness messages downstream, and detection of
  possible blocking of staleness notifications.
\end{theorem}
